Verifying Demonstrations

### 2021-06-16 paper/protocol.tex
Clarifies protocol intro further

The entities involved in our protocol are participants and (count) verifiers.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and 
  disseminated it to others.
  Anyone can do this, but in general, there is only one organizer.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for their presence.
\item A \emph{witness} provides proofs to protesters which state that they indeed participated, constructed such that the proofs are verifiable by 
  third parties.
\end{enumerate}
After the protest, anyone can be a verifier (universal verifiability, 
\cref{security-properties}), \ie count the number of participants (of the 
protest and the protocol) or verify anyone else's count given the relevant meta 
data (which protest, location, time, and witness parameters used in the
count). We refer to anyone counting or verifying a count as the
verifier; the process is the same.

>>>>

The entities involved in our protocol are participants and (count) verifiers.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and 
  disseminated it to others.
  Anyone can do this, but in general, there is only one organizer.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for their presence.
\item A \emph{witness} provides proofs to protesters which state that they indeed participated, constructed such that the proofs are verifiable by 
  third parties.
\end{enumerate}
After the protest, anyone can be a verifier (universal verifiability, 
\cref{UniversalVerif} in \cref{verifiability-properties}), \ie count the number 
of participants (of the protest and the protocol) or verify anyone else's count 
given the relevant meta data (which protest, location, time, and witness 
parameters used in the
count). We refer to anyone counting or verifying a count as the
verifier; the process is the same.

Any participant can verify their inclusion (individual verifiability, 
\cref{IndividualVerif} in \cref{verifiability-properties}) by repeating the 
count (the verification process) but also checking that their proof is included 
while counting.
